Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-22 paper/cfg-to-nfa.tex
minor rewrites

\added{The resulting automaton has edges labeled with \acar, \acdr\ and
\clazy\ only.  For our example, the  NFA for \var{\Df{\length}{1}} is 
\nfaD.
In this  automaton, for every  edge labeled  \clazy, we
check if the source node of the edge  has a path to a final state.  If
it does, we mark the source node  as final. For \var{\Df{\length}{1}}, we get \nfaDF. Finally, we remove all the
edges labeled \clazy\  and convert the automaton  into a deterministic
automaton.   These steps  effectively implement  the $\hookrightarrow$
simplification rules for \bcar, \bcdr, and
\clazy\ to  obtain forward access paths.   The final DFA obtained for \var{\Df{\length}{1}} is \dfaD.}
While checking for  liveness during
garbage collection,  a forward  access path  is valid  only if  it can
reach a final state.
This  expectedly says  that
for  a  demand  $\sigma_{\length}$,   the  liveness  of  the  argument
of \length\ is $\acdr^{*}$ (the spine of the list is traversed).

\newcommand{\dfaE}{%
  \scalebox{.70}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(0,-2)(35,8)
     \putnode{t0}{origin}{0}{0}{} 
     \putnode{t1}{t0}{8}{0}{\pscirclebox{\mbox{$q_0$}}} 
     \hspace{5mm} 
   \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{$q_1$}}}
   \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} 
   \putnode{l0}{t1}{5}{2}{\clazy}
   \putnode{tD1}{t2}{12}{0}{\pscirclebox[doubleline=true]{\mbox{$q_2$}}} 
   \psset{arrows=->} \ncline{t2}{tD1} 
   \putnode{l1}{t2}{5}{2}{\bcar}
   \nccurve[angleA=45,angleB=135,ncurv=2,nodesep=-1]{tD1}{tD1} 
   \putnode{lD1}{tD1}{0}{7}{\acdr}
\end{pspicture} 
  }}

\newcommand{\dfaF}{%
  \scalebox{.70}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(3,-2)(24,3)
     \putnode{t0}{origin}{2}{0}{} \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{$q_0$}}} 
       \hspace{5mm} 
        \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{$q_1$}}}
         \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} \putnode{l0}{t1}{5}{2}{\clazy}
         \end{pspicture}
         }
         }

\newcommand{\dfaG}{%
  \scalebox{.70}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(3,-2)(10,3)
    \putnode{t0}{origin}{2}{0}{} \putnode{t1}{t0}{7}{0}{\pscirclebox{\mbox{$q_0$}}} \hspace{1mm} \psset{arrows=->} \ncline{t0}{t1}
      \end{pspicture}
      }
      }

>>>>

\added{The  resulting   automaton  has   edges  labeled   with  \acar,
  \acdr\   and  \clazy\   only.   For   our  example,   the  NFA   for
  \var{\Df{\length}{1}} is  \nfaD.  In this automaton,  for every edge
  labeled \clazy, we check  if the source node of the  edge has a path
  to a final state.  If it does, we mark the source node as final. For
  \var{\Df{\length}{1}}, we get \nfaDF, in which $q_0$ becomes a final
  state. Finally, we remove all  the edges labeled \clazy\ and convert
  the  automaton   into  a   deterministic  automaton.    These  steps
  effectively implement the $\hookrightarrow$ simplification rules for
  \bcar, \bcdr, and \clazy\ to obtain forward access paths.  The final
  DFA obtained  for \var{\Df{\length}{1}}  is \dfaD.}   While checking
for liveness during garbage collection, a forward access path is valid
only if it can  reach a final state.  This expectedly  says that for a
demand $\sigma_{\length}$, the liveness of the argument of \length\ is
$\acdr^{*}$ (the spine of the list is traversed).

\newcommand{\dfaE}{%
  \scalebox{.70}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(0,-2)(35,8)
     \putnode{t0}{origin}{0}{0}{} 
     \putnode{t1}{t0}{8}{0}{\pscirclebox{\mbox{$q_3$}}} 
     \hspace{5mm} 
   \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{$q_4$}}}
   \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} 
   \putnode{l0}{t1}{5}{2}{\clazy}
   \putnode{tD1}{t2}{12}{0}{\pscirclebox[doubleline=true]{\mbox{$q_5$}}} 
   \psset{arrows=->} \ncline{t2}{tD1} 
   \putnode{l1}{t2}{5}{2}{\bcar}
   \nccurve[angleA=45,angleB=135,ncurv=1.5,nodesep=-1]{tD1}{tD1} 
   \putnode{lD1}{tD1}{0}{7}{\acdr}
\end{pspicture} 
  }}

\newcommand{\dfaF}{%
  \scalebox{.70}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(3,-2)(24,3)
     \putnode{t0}{origin}{2}{0}{}
     \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{$q_3$}}} 
     \hspace{5mm} 
     \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{$q_4$}}}
     \psset{arrows=->} \ncline{t0}{t1} 
     \ncline{t1}{t2} 
     \putnode{l0}{t1}{5}{2}{\clazy}
    \end{pspicture}
  }
}

\newcommand{\dfaG}{%
  \scalebox{.70}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(3,-2)(10,3)
      \putnode{t0}{origin}{2}{0}{}
      \putnode{t1}{t0}{7}{0}{\pscirclebox{\mbox{$q_3$}}} 
      \hspace{1mm} \psset{arrows=->} 
      \ncline{t0}{t1}
    \end{pspicture}
  }
}
